Water Management

### 2020-01-23 Paper/paper.tex
begin adding some theory

	\section{Main Part}
	\subsection{Theory}
	(Für die Präsentation)

>>>>

	\section{Main Part}
	\subsection{Theory}

	In this paper, the theoretical knowledge obtained in the seminar shall be applied.

	\subsubsection{Quadrature}
	In many computational applications, formulas 	are used to calculate values of any kind. For example, let the flow of water through a pipe be

	\begin{equation}
	f(t) = sin(\pi t), \; t \in [0,1]
	\end{equation}

Now, it's trivial to compute the flow at any given time using code, simply by implementing the formula as given above. However, if we want to compute the amount of water flowing through the pipe in the interval $[0.25, 0.5]$, we can not calculate that directly, as we would have to know the antiderivative of $f(t)$. In this example, this might be solved analytically

---

	(Für die Präsentation)
